\chapter{Wishful Thinking}

\textit{Whoossshhh...}\\

The wind buffetted dangerously through Adrienne's short curls. 
She knew exactly how high up she stood on this building, and she did not need to look down to confirm it.
The queazy feeling in her stomach settled somewhat as she lowered herself in a crouch, 
but even the steadying index finger with which she caressed these red clay roof tiles would do little to slow the pounding of her heart.\\

Some rogue she was.\\

The clatter of loose dirt and tile under her foot siezed her rapidly beating heart to a short stop.
Luckily, the sliding stopped too.
Adrienne breathed a deep sigh in relief. 
And frustration.\\

Steeling her eyes, she mentally tested the grip of her rubber-soled shoes on the tiles. 
Her fingers wrapped around a small charm that hung from the band on her wrist.\\

The cat's paw-pad. An amulet of agility.\\

And so, like a feline spirit possessed her, Adrienne stole across the tiles with ever-increasing confidence and speed.
She would need the speed when she got to the edge of the roof.
Hopefully the boon of the amulet would be enough.\\

The sloping graduated slowly, and Adrienne found herself able to straighten into a run.\\

\textit{Adrienne.}\\

Knees pulled to the sky and shoulders drew back as Adrienne lengthened her stride.
The wind pulled like a gale through her rogueish robes, her speed locking in her focus.\\

\textit{Adrienne.}\\

The rooftop of the second building loomed. 
Taller, steeper than she imagined it would be.
Adrienne did not know what she expected otherwise; government buildings always had a tendency to sport those awful gothic-style roofs. \\

Didn't they?\\

\textit{Adrienne!}\\

Her thoughts launched her toward the very roof she was contemplating, the rush of wind beneath her as she sailed across the empty late-night main street.
The amulet slipped from her fingers, hitting against the wrist it was tethered to.
Arms and legs flailed like windmills as Adrienne did what she could to extend her time in the air before reaching a mistimed landing \dots\\

``ADRIENNE!''\\

Feet met the floor followed closely by knees and hands.\\

``ow...''\\

``Adrienne, what the hell, dude? It's like, three in the fucking morning."\\

Alan's blazing brown eyes, normally accusing or concerned at his flatmate's increasingly singular antics, were now devoid of whatever sympathy there would have been in the weeks before.
"Blazing" would also be the incorrect description at this point.
It would imply a sense of energy.\\ 

To be frank, Alan's eyes, pallid skin, disshevelled hair and sourly impassive expression altogether painted an accurate image of a young man that was thoroughly dead inside.\\

``Sorry.'' Adrienne apologised sheepishly, not making eye contact. 
Instead she shifted her gaze to the clock sitting on her small desk.
"02:53" the red seven-segment displays shone.
The diminutive electronic was barely visible among the clutter of sticky notes and papers.\\

"Are you ready for tomorrow?" She asked, hoping to change the subject. She knew he was awake until now too. 
Engineering students had a very strange way of coping with exam season. 
At least "studying", or sitting frozen before the same set of notes until your eyes glazed over as Alan did, was healthier than most.\\

Healthier than getting "lost", as Adrienne called it. 
Which was happening more and more lately.
She refused to grow too concerned about it.
She would not normally be, at least not for herself.
Adrienne was more concerned at Alan's increasingly low tolerance for her, and how she felt helpless to fix that.\\

"I would be, if I could get some flipping sleep. Go to bed, Adrienne. Or study. Or actually, no. Go to sleep."\\

"Sorry, Alan, I..."\\

"Go to sleep. I will personally drag you to the green-roofed house if you don't."\\

A note of care could indeed be found in Alan's voice --- but it was for nought. Adrienne was quite wounded and mortified by Alan's threat.
Well, Alan's "threat". Alan did think that Adrienne's daydreaming was increasingly maladaptive to the point of concern, even for an exam season.
But what concerned him more than her behaviour at the moment was the possibility of losing out on whatever precious little sleep either of them would be getting before the exam the next day.\\

Well...\\

Later that same morning.\\

"... sure. Sorry."\\

Alan made no move to acknowledge Adrienne's apology.
Instead, he simply gestured from the clock to the bicycle helmet hanging on Adrienne's bedroom wall.\\

"Bike or lift?"\\

Adrienne slowly stood from where she landed on the floor. 
She considered Alan's offer carefully. 
Normally, she would prefer cycling; it clears her head.
However, with most of her study time procrastinated away in a flurry of home-brewing a new and wishful DragonRPG campaign that culminated in RP'ing as a rogue at midnight...\\

"Lift, please." Adrienne supplied quietly.\\

The extra time to memorise some of her flashcards would likely do little to increase her chances of passing, but it would ease some anxiety.\\

"You will be up and ready at seven. Go to sleep."\\

Alan's retreating footsteps punctuated the exhausted silence that he left behind.\\

Adrienne's eyes fell on the clock again. 
03:00 on the dot. 
This would leave her with only around three and a half hours of sleep. 
If she were lucky.
The most likely scenario would be lying awake for forty-five minutes to an hour before dragging herself back to wakefulness just as she reached REM sleep.\\

The little clock grew double and swam in her glazed vision.
She let the red light of the tiny display bear into her purposely unfocused eyes.
Thoughts felt like they would rather fish for their purpose in peanut butter than materialise in her mind.\\

A rueful chuckle escaped her lips at the image the thought conjured.
A vision of hundreds of tiny little blue sugar-sprites desperately grasping for salvation as they inevitably dissolve in the impossible bottle of peanut butter.\\

Was it a glass bottle or a plastic one?\\

\textit{Shit, Adrienne. Focus. Sleep.}\\

She rocked back and forth on her heels a moment longer, eyes still glazed and unfocused.
Her attention returned to the clock.\\

03:21, the blurry haze of double-vision digits read.\\

Did the time really pass that quickly?
At this point she would be far better off just staying awake and hoping she does not pass out mid exam paper.
Good thing she opted for a lift with Alan rather than taking the bicycle.
Flip.
Imagine cycling in this state.
That would be a hazard, for sure.\\

03:32.\\

Adrienne shuddered and let her eyes refocus.
The double vision took a little longer than usual to snap back to normal.\\

Stay up, or go to sleep?
What would three hours do? 
Especially if they would likely be whittled down to two. 
One and a half if she kept dragging herself to bed this slowly.
One if she has to wake up earlier than she estimated.\\

One hour of sleep is useless.
If she will even get that.\\

\textit{Go. To. Sleep.}\\

Well, she \textit{would} get absolutely nothing if she carried on like this.\\

Damn it. Why couldn't she just \textit{move}?\\

Something on her desk moved instead.
With a yelp, Adrienne whipped her head around to stare at the shelf above her desk.\\

\textit{"Adriennee...."} came a half-awake, decidedly sleeptalking groan of scolding from the vague direction of Alan's room.
She did not give it as much heed as she wanted to, though it did make her cringe at her reluctance to oblige to a very simple and very healthy request to just... sleep.\\

She scanned the shelf for the source of the movement she was sure she had just seen.
What would normally be occupied with textbooks was instead populated with an extensive collection of DragonRPG manuals and lovingly painted miniatures.
All of them perfectly, infuriatingly, still.
One of these miniatures drew her attention in particular.\\

"Sir Mouse?" Adrienne whispered, her voice barely above a breath.\\

The miniature of a Mousefolk Paladin, resplendent in lovingly rendered armour that showed off Adrienne's first attempt at under-shading, stood perfectly still on the edge of the shelf.\\

He was supposed to be on her desk, next to her pencil case. 
Not on the shelf.\\

The dour expression on that still, plastic face did nothing to explain itself. 
All Adrienne felt was a severe sense of \textit{judgement}.
Like Sir Mouse, the Mousefolk Paladin with an Oath of Journalistic Excellence (homebrew subclass), was more disappointed in her at this moment than any other person ever could have been.\\

Adrienne covered her face, pressing against her closed eyelids until faint, kaleidescopic static appeared in her vision.
She took a deep breath and ambled to the bed she had just jumped off from. 
A bed that doubled as a roof in her overactive imagination moments before.\\

Adrienne did not even change her clothes.
She had lost too much time already.\\

As she pulled the covers over her, she glanced one more time at the Mousefolk Paladin staring down at her from above before turning off her lamp.\\

"Sorry."
