\chapter{Prologue}

\lettrine{``When}{last have you flown, Osthryn"?}\\
She turned to look at Silovar, their fingers gently dancing between commitment to real contact and hesitation to bridge the narrow gap between their hands as they leaned back on the grass side-by-side.
The view over Mountainkeep below them painted the perfect picture of a city built by people who expected only conflict with people.
The houses' roofs were brightly tiled, the streets were open and broad, the Keep was built high on the mountainside, and the city walls confidently shielded against any onslaught that could come from the horizon and below.\\

Dragons were a legend of creation here.
The myth of the Four and their Shattered Stones that laid the foundation of the world was oft-repeated in nursery rhymes and bedtime stories with wonder and fearless reverence.
The imagery of Dragons flying in the skies above warned children that their integrity was observed, and comforted the well-behaved with the knowledge that at any time a Dragon could see harm befalling them and intervene.
Scales worked into armour, items of clothing, jewelry, and symbols of the proud creatures abounded in the courts of the Keep and the wide, peaceful city streets.\\

This was not the case in the North.
Legends of destruction, greed, and ruthlessness permeated the Ice-wind Isles's consciousness.
Vibrantly tiled roofs did not exist, and roads either twisted in an abundance of alleyways or hugged close to large landscape features.
Houses were built into mountainsides and hillsides, and where they could not build fully underground, they lifted the ground overhead.\\

Where in the South Dragons took on skin and warm blood to be among people for the love of it, in the North they took it on to atone for millennia of sins.
A Dragon's flight was the most forbidden action a Northern Dragon could take. 
In all her 400 years, Osthryn could count on her fingers the number of times she was simply in her scales, and each time she was met with swift and severe discipline.\\

She looked into Silovar's eyes, the silver-blue shining with genuine expectation and perfect innocence of his question's weight.\\

``It's... been a while," She cautiously admitted, a half-truth.\\


\cleardoublepage   % Make sure contents page starts on right-side page